Future Cosmic Microwave Background delensing with galaxy surveys.

### 2017-07-05 Notes/galaxy_delensing.tex
typos

An ambitious program for a generation 4 ground CMB experiment is currently under planning \cite{abazajian:2016}. 
Moreover, satellite and balloon experiments have been proposed and have the potential to extend the accessible B-mode measurement to the largest scales.
Here we follow \cite{abazajian:2016} and assume a CMB-S4 ground experiment with  with a level of noise of \textcolor{red}{$1\mu$K-arcmin} with a \textcolor{red}{1 arcmin} beam.
By the mid 2020s several next generation of LSS survey will be online. Here, as an example for future optical galaxy surveys we add LSST \cite{lsst-science-collaboration:2009} to the CMB lensing tracers. We test that other experiments like Euclid \cite{laureijs:2011} and WFIRST \cite{spergel:2013} will have similar delensing performance. Even if they will observe similar part of the sky, because of the different  strength and weakness of this experiments  
it will still important to combined them efficiently.
We also consider a radio continuum survey modeled following the SKA planned experiment. Radio continuum observation of the 21 cm line is in its early stage and several experimental and analysis challanges 
need to be overcome. However this technique has the potential to map LSS with relatively low noise up to redshift $z=6$.

@@

A tomographically binned LSST-like experiment will be a very efficient CMB lensing tracer. Indeed it will be more than 70\% correlated with CMB lensing for all the scales $\ell<600$ a performance similar to a Stage 3 CMB internal reconstruction.
SKA very new but potentially amazing
With SKA and LSST, for the first we will have LSS tracers way more efficient than the CIB.
Even if galaxy survey will improve dramatically the CMB internal reconstruction will still be the main source of delensing. This, having a perfect kernel overlap with the true lensing potential we will benefit for the very low level of noise of CMB S4 experiments.
CMB S4 delensing will probably be limited by small secondary effect like foregrounds contamination, missing modes due to filtering etc.

>>>>

An ambitious program for a generation 4 ground CMB experiment is currently under planning \cite{abazajian:2016}. 
Moreover, satellite and balloon experiments have been proposed and have the potential to extend the accessible B-mode measurement to the largest scales.
Following \cite{abazajian:2016} we assume a CMB-S4 ground experiment with a level of noise of \textcolor{red}{$1\mu$K-arcmin} and a \textcolor{red}{1 arcmin} beam.
Furthermore, by the mid 2020s, several next generation of LSS survey will be online. Here, as an example for future optical galaxy surveys, we add LSST \cite{lsst-science-collaboration:2009} to the CMB lensing tracers. We test that other experiments like Euclid \cite{laureijs:2011} and WFIRST \cite{spergel:2013} have similar delensing performance. Even if they will observe similar part of the sky, because of the different strength and weakness of this experiments it will still be important to consider all of them and combine them efficiently.
We also consider a radio continuum survey modeled following the SKA planned experiment. Radio continuum observation of the 21 cm line is in its early stage, and several experimental and data-analysis challenges need to be overcome. 
However, this technique has the potential to map LSS with relatively low noise up to redshift $z=6$.

@@

A tomographically binned LSST-like experiment will be a very efficient CMB lensing tracer. Indeed it will be more than 70\% correlated with CMB lensing for all the scales $\ell<600$, a performance similar to a Stage-3 CMB internal reconstruction.
SKA very new but potentially amazing
With SKA and LSST, for the first we will have LSS tracers with a higher delensing efficiency than the CIB.
Even if galaxy survey will improve dramatically the CMB internal reconstruction will still be the main source of delensing. This, having a perfect kernel overlap with the true lensing potential we will benefit for the very low level of noise of CMB S4 experiments.
CMB S4 delensing will probably be limited by small secondary effect like foregrounds contamination, missing modes due to filtering etc.
